A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-09-19 manuscript/supplementary.Rmd
add ability to include supplementary tables as excel

```{r}
supplementary <- read_rds("supplementary.rds")
sfigs <- supplementary$sfigs
```

@@

>>>>

```{r}
supplementary <- read_rds("supplementary.rds")
sfigs <- supplementary$sfigs
stables <- supplementary$stables
refs <- supplementary$refs
```

@@

```{r, results="asis"}
stables %>% pmap(dynbenchmark:::show_table, ref_type = "stable") %>% walk(cat)
```
